---
title: "ISER Report: Introduction"
author: "Office of Research, Planning and Institutional Effectiveness"
date: "`r Sys.Date()`"
output: word_document
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(flextable)
library(officer)

load("../is_standards.RData")
load("../entable.RData")
load("../jobs.RData")
load("../demo.RData")
load("../labor_data.RData")
set_flextable_defaults(font.size = 9)

```


# Introduction

## College History

San José City College is celebrating its Centennial this year, 2021. For 100 years, SJCC has been a symbol of hope for students and an innovative leader in providing educational and career pathways to generations of families living in California's third-largest city. SJCC has built a legacy of educational and institutional excellence by adapting to the rapid changes that have transformed the Valley of Hearts Delight into Silicon Valley, a major driver of the state, national, and global economies.

The College was founded in 1921 and it is located southwest of the City of San José, California. The College is one of two accredited institutions governed by the Board of Trustees of the San José-Evergreen Community College District (SJECCD). The District, located in northeastern Santa Clara Valley, includes all of the City of Milpitas and part of the City of San José. The second college in the SJECCD, Evergreen Valley College (EVC), is located fifteen miles southeast of SJCC, in a suburban area of the City of San José and adjacent to Montgomery Hill Park. The District includes 300 square miles. The San José/Evergreen Community College District officially became an independent college district in
1963.

San José City College (SJCC) opened its doors in 1921 to a class of 86 students. It is the oldest community college in Santa Clara County and one of the 10 oldest in California. Today, SJCC, which includes the Milpitas Extension, enrolls more than 16,000 students annually. The campus, which is federally designated as a Hispanic Serving Institution (HSI) and Asian American Native American Pacific Islander Serving Institute (AANAPISI), comprises one of the most diverse student bodies within the California Community College System.

For 61 years the campus has been located in downtown San José. Through the 1960’s and 1970’s San José City College owned more property than it does currently. The boundaries of SJCC stretched east from Bascom Avenue to Menker Avenue. Portions of this property were sold off for the development of Interstate 280 and traded to incorporate the current land where a multipurpose field currently resides.

Bond measures in 1998, 2004, 2010 and 2016 have supported much needed facilities construction: the Cesar Chavez Library, Parking Garage, Career Technology, Technology Center, Multi-Disciplinary and Carmen Castellano Fine Arts Center, Student Center, Jaguar Athletics Complex, Science/Math, and renovations of the Business, Cosmetology, Reprographics, Theater buildings. Construction is underway for a new Maintenance and Operations and Career Education Complex. Additionally, plans are underway for a new Jaguar Multicultural Building.

SJCC’s Milpitas Extension is a unique collaboration between the Milpitas Unified School District (MUSD) and the San José Evergreen Community College District (SJECCD) to establish an Educational Innovation Lab.  Since the conception of this joint effort, the landscape has changed allowing capacity to implement innovative programs, have a fluid operation, and to develop new academic pathways that will shorten the time to degree, enhance the student experience, and develop best practices in dual enrollment, and collaborative efforts between a California Community College and K–12 District.

The Community College Center for Economic Mobility (CEM), located in the District location in downtown San José, complements the instructional programs of both colleges in the SJECCD. Established in 1988 as a self-supporting enterprise, the Institute has partnered with a diverse array of companies applying performance-based solutions to ensure effective training. In addition, CEM provides educational and training opportunities for working professionals and job seekers to keep them current in the highly competitive Silicon Valley job market. The offerings of WI include a range of online, self-paced industry certificates for career development, personal enrichment fee-based community service classes, contract education to businesses, and noncredit adult education associated with regional
partnerships.

As we look back at SJCC's history, it is also vitally important that we honor the history of the land on which we stand and recognize that our community continues to benefit from the use and occupation of the Ohlone people's unceded ancestral homeland. Consistent with our values of inclusion and diversity, we respect and honor the College's relationship with the San Francisco Bay Area's original people. They continue to flourish in our communities, and we affirm their sovereign rights as first peoples.

Finally, we are proud to say that the future of SJCC looks bright and full of opportunity. We aspire, through excellence, to be the very best community college in Silicon Valley. We will continue to strive to build and strengthen our teams of students, faculty, alumni, and community partners.


## Student Enrollment Data 

### Overall Enrollment Trend

The college's overall enrollment (headcount) has declined in the last 5 years after a small increase in 2018-2019. Given the impact of COVID-19 pandemic and the statewide enrollment decline, this is not surprising. The overall annual headcount has declined 16% from 2017-18 to 2021-22. This decline is reflected throughout the enrollment trend data.


```{r, ft.align='left'}
annual %>% 
    filter(Metric == "Overall:" | Metric == "Credit Students:" | Metric == "Noncredit Students:" | Metric == "Headcount") %>% 
  flextable() %>% 
  set_caption("Annual Student Headcount", 
              autonum = run_autonum(seq_id='tab', bkm='hc')) %>% 
  footnote(j=1, value=as_paragraph("Source: SJCC Internal Data Warehouse"),
           ref_symbols=c(""), part = "header") %>% 
  width(j=1, width=2) %>% 
  #if including ftes and sc, these five lines need to be used so that they affect the subheadings
  # surround(i = 5, part = 'body', border.top = fp_border()) %>% 
  # surround(i = 9, part = 'body', border.top = fp_border()) %>% 
  # bold(i=1, part='body') %>% 
  # bold(i=5, part='body') %>%
  # bold(i=9, part='body') %>% 
  surround(i = 3, part = 'body', border.top = fp_border()) %>% 
  surround(i = 5, part = 'body', border.top = fp_border()) %>% 
  bold(i=1, part='body') %>% 
  bold(i=3, part='body') %>%
  bold(i=5, part='body') %>% 
  footnote(j=1, value=as_paragraph("A student is counted as credit/noncredit if they take at least one course in that type. Note that some students enroll in both credit and noncredit courses during the academic year, so they are included in both the credit and noncredit figures. Because of this, the sum of credit and noncredit headcounts does not equal the overall headcount."),
           ref_symbols=c(""), part = "header")
#### have the seatcount and FTES ready, but remove from the discussion here. We may put them back in later. Let me know if you have any questions on this.
```



### Credit Enrollment Trends and Student Composition

This section describes the credit enrollment trends by various student attributes. Data are from Fall terms between Fall 2017 and Fall 2021. It includes all students enrolled in at least one credit course. The data are extracted from the district's internal database by the Office of Research, Planning and Institutional Effectiveness. 

The five-year Fall credit headcount reveals a pattern already described above. While the decline in the last two years is largely due to the impact of the COVID-19 pandemic, the enrollment decline had began in Fall 2019. From Fall 2018 to Fall 2019, the credit headcount declined by 5%.  Over the last five years (from Fall 2017 to Fall 2021) , it declined 19%. The headcount averaged over the last five years is 8,841.

```{r, ft.align='left'}
fall_hc %>% 
  flextable() %>% 
  set_caption("Unduplicated Overall Headcount, Fall Terms", 
              autonum = run_autonum(seq_id='tab', bkm='fhc')) %>% 
  footnote(j=1, value=as_paragraph("Source: SJCC Internal Data Warehouse"),
           ref_symbols=c(""), part = "header") %>% 
  width(width=.8)
```

On average, 62% of credit students are continuing students in Fall terms. While enrollment has decreased, the percentage of continuing students enrolled in credit classes has increased, going from 57%. On the other hand, the percentage of new students had decreased from 21% to 14%. 

Nearly 17% of credit students are new students, and 12% of credit students are returning students. Approximately 8% percent of credit students are K-12 students dual-enrolled in high-school and college courses.  

```{r, ft.align='left'}
fall_type %>% 
  flextable() %>% 
  set_caption("Share of Fall Credit Students by Student Type", 
              autonum = run_autonum(seq_id='tab', bkm='fthc')) %>% 
  footnote(j=1, value=as_paragraph("Source: SJCC Internal Data Warehouse"),
           ref_symbols=c(""), part = "header") %>%
  width(j=1, width=1.3) %>% 
  width(j=7, width=1) %>% 
  align(j=c(2:7), align = 'right', part = 'all')

```

Earning an AA degree for transfer to a four-year college is the most common educational goal among credit students in Fall terms, with 40% of credit students listing this as their primary educational goal. Around 11% of students stated their goal was to transfer to a four-year college without an AA, and another 10% were undecided on their goal. 

Around 50% of students plan on transferring to a four-year college with or without an AA degree. Similarly, around 48% of credit students plan on earning an AA degree regardless of whether they transfer to a four-year college.

Over 70% of students have a goal of transfer to four-year institutions or earning a degree or certificate.


```{r, ft.align='left'}
fall_goal %>% 
  #pivot_wider(names_from="Fall Term", values_from = "Headcount") %>% 
  flextable() %>% 
  set_caption("Share of Fall Credit Students by Educational Goal", 
              autonum = run_autonum(seq_id='tab', bkm='fghc')) %>% 
  footnote(j=1, value=as_paragraph("Source: SJCC Internal Data Warehouse"),
           ref_symbols=c(""), part = "header") %>% 
  width(j=1, width=2) %>% 
  align(j=c(2:7), align = 'right', part = 'all')
```

The majority of credit students across all five years were female, with an average population of 57% female students and 42% male students. 
The percentage of female students has risen 5 percent in the past five years, while the percentage of male students has dropped.

```{r, ft.align='left'}
fall_gender %>% 
  #pivot_wider(names_from="Fall Term", values_from = "Headcount") %>% 
  flextable() %>% 
  set_caption("Share of Fall Credit Students by Gender", 
              autonum = run_autonum(seq_id='tab', bkm='fgehc')) %>% 
  footnote(j=1, value=as_paragraph("Source: SJCC Internal Data Warehouse"),
           ref_symbols=c(""), part = "header") %>% 
  width(j=7, width=1.1) %>% 
  align(j=c(2:7), align = 'right', part = 'all')
```

Approximately 45% of credit students in Fall terms were Latinx. This has remained constant throughout the past five years. The percentage of Asian credit students has slightly increased from 23% in 2017 to 27% in 2021. Likewise, the percentage of White credit students has decreased from 14% to 11%. The percentage of Black credit students has stayed steady at around 5% over the past five years.  

```{r, ft.align='left'}
fall_race %>% 
  #pivot_wider(names_from="Fall Term", values_from = "Headcount") %>% 
  flextable() %>% 
  set_caption("Share of Fall Credit Students by Race/Ethnicity", 
              autonum = run_autonum(seq_id='tab', bkm='frhc')) %>% 
  footnote(j=1, value=as_paragraph("Source: SJCC Internal Data Warehouse"),
           ref_symbols=c(""), part = "header") %>% 
  width(j=1, width=1.6) %>% 
  align(j=c(2:7), align = 'right', part = 'all')
```

Around 46% of credit students in Fall terms are between the ages of 18 and 24. Then, 33% of credit students are between 25 and 39. While nearly 80% of credit students between 18 and 39 years old, there are also sizable populations of students over 40 and under 18.

```{r, ft.align='left'}
fall_age %>% 
  #pivot_wider(names_from="Fall Term", values_from = "Headcount") %>% 
  flextable() %>% 
  set_caption("Share of Fall Credit Students by Age", 
              autonum = run_autonum(seq_id='tab', bkm='fahc')) %>% 
  footnote(j=1, value=as_paragraph("Source: SJCC Internal Data Warehouse"),
           ref_symbols=c(""), part = "header") %>% 
  width(j=1, width=.8) %>% 
  width(j=7, width=1) %>% 
  align(j=c(2:7), align = 'right', part = 'all')
```
The college serves multiple special student populations with the largest group being the First Generation college students. The college serves a sizable group of students with disability, the number served has declined significantly in the last two years, most likely due to the impact of the COVID-19 pandemic. On the other hand, the college has seen an increase in Foster Youth, UMOJA and Veteran students over the last five years.


```{r, ft.align='left'}
sp_hc %>% flextable() %>% 
  set_caption("Unduplicated Headcount of Special Populations, Fall Terms", 
              autonum = run_autonum(seq_id='tab', bkm='special')) %>% 
  footnote(j=1, value=as_paragraph("Source: CCC Chancellor's Office Data Mart"),
           ref_symbols=c(""), part = "header") %>% 
  align(j=2:6, align = "right", part = "all") %>% 
  width(j=1, width=3)
```
### Noncredit Enrollment Trends and Student Composition


The vast majority of noncredit students are enrolled in ESL classes. 

```{r, ft.align='left'}
#subject area (split crs_name into dept, #)
fall_ncsubject %>% 
  flextable() %>% 
  set_caption("Share of Fall Noncredit Students by Subject Area", 
              autonum = run_autonum(seq_id='tab', bkm='fahc')) %>% 
  footnote(j=1, value=as_paragraph("Source: SJCC Internal Data Warehouse"),
           ref_symbols=c(""), part = "header") %>% 
  width(j=7,width=1.1) %>% 
  align(j=c(2:7), align = 'right', part = 'all') %>% 
  footnote(j=1, value=as_paragraph("Students who enrolled in multiple noncredit subjects are included in the percentages for all relevant noncredit subjects."), ref_symbols=c(""), part = "header")


```


Female students make up the majority of noncredit students with 67% of the noncredit student population being female over the past five years. In contrast, male students make up only 30% of the noncredit student population.
In Fall 2020, female students comprised almost 75% of the noncredit student population, a 10% increase than the year before. 

```{r, ft.align='left'}
#gender
fall_ncgender %>% 
  flextable() %>% 
  set_caption("Share of Fall Noncredit Students by Gender", 
              autonum = run_autonum(seq_id='tab', bkm='fgehcnc')) %>% 
  footnote(j=1, value=as_paragraph("Source: SJCC Internal Data Warehouse"),
           ref_symbols=c(""), part = "header") %>% 
  width(j=7,width=1.1) %>% 
  align(j=c(2:7), align = 'right', part = 'all')



```

On average, 34% of noncredit students in Fall terms were Asian, while 31% were Latinx. White students made up 15% of the noncredit student population, and Black students comprised around 4% on average.

In Fall 2020, the percentage of noncredit White students rose 12 percent from Fall 2019, while the percentage for noncredit Asian students dropped 10 percent. Similarly, the percentage of Latinx noncredit students dropped around 8 percent from Fall 2018 to Fall 2019. 

```{r, ft.align='left'}
#race
fall_ncrace %>% 
  flextable() %>% 
  set_caption("Share of Fall Noncredit Students by Race/Ethnicity", 
              autonum = run_autonum(seq_id='tab', bkm='frhcnc')) %>% 
  footnote(j=1, value=as_paragraph("Source: SJCC Internal Data Warehouse"),
           ref_symbols=c(""), part = "header") %>% 
  width(j=7,width=1.1) %>% 
  width(j=1,width=1.6) %>% 
  align(j=c(2:7), align = 'right', part = 'all')

```

Students aged 25 to 39 make up 42% of the noncredit student population on average. In contrast with the credit student population, 40% of the noncredit student population is 40 years old or over. In total, over 80% of the noncredit student population is 25 or older. 
Only 15% of the noncredit population is between 18 and 24. 

```{r, ft.align='left'}
#age
fall_ncage %>% 
  flextable() %>% 
  set_caption("Share of Fall Noncredit Students by Age", 
              autonum = run_autonum(seq_id='tab', bkm='fahcnc')) %>% 
  footnote(j=1, value=as_paragraph("Source: SJCC Internal Data Warehouse"),
           ref_symbols=c(""), part = "header") %>% 
  width(j=7,width=1.1) %>% 
  width(j=1,width=.9) %>% 
  align(j=c(2:7), align = 'right', part = 'all')

```




## Labor Market Data 

At a broad level, the top industries in the Greater Bay Area are Health Care and Social Assistance and Professional, Scientific, and Technical Services.

```{r, ft.align='left'}
broad_ten %>% flextable() %>% 
  flextable::set_formatter("Share of Total Employment" = function(x) sprintf("%.001f%%", x*100)) %>% 
  set_caption("Top Industries by Employment (Greater Bay Area, 2020 Q3)", autonum = run_autonum(seq_id='tab', bkm='broadten')) %>% 
  footnote(j=1, value = as_paragraph("Source: JobsEQ, via Hanover Research"), ref_symbols=c(""), part = "header") %>% 
  width(j=1, width = 4.5) %>% 
  width(j=2, width=2)
```

More than 10 percent of workers are employed in each of these two broad industries. At a more detailed level, employment after restaurants is concentrated in several high tech industries, schools, and hospitals (see the top industries by employment table). 

```{r, ft.align="left"}
topten %>% flextable::flextable() %>% 
  flextable::set_formatter("Share of Total Employment" = function(x) sprintf("%.001f%%", x*100)) %>% 
  width(j=1, width = 4.5) %>% 
  width(j=2, width=2) %>% 
  set_caption("Top Industries by Employment  (Greater Bay Area, 2020 Q3)", autonum = run_autonum(seq_id='tab', bkm='topten')) %>% 
  footnote(j=1, value = as_paragraph("Source: JobsEQ, via Hanover Research"), ref_symbols=c(""), part = "header")
```

All top 10 Bay Area tech industries by share of employment have positive 10-year projected growth.

```{r, ft.align="left"}
toptech %>% flextable::flextable() %>% 
  set_caption("Top Bay Area Tech Industries  (Greater Bay Area, 2020 Q3)", autonum = run_autonum(seq_id='tab', bkm='toptech')) %>% 
  flextable::set_formatter("Projected Growth, 2020-2030" = function(x) sprintf("%.001f%%", x*100)) %>% 
  flextable::set_formatter("Share of Total Employment" = function(x) sprintf("%.001f%%", x*100)) %>% 
  flextable::set_table_properties(width = .5, layout='autofit') %>% 
  footnote(j=1, value = as_paragraph("Source: JobsEQ, via Hanover Research"), ref_symbols=c(""), part = "header")

```

Also, the Greater Bay Area is projected to have an employment undersupply for occupations in business, technology, and healthcare including software developers, nurses, and managers while it is also projected to have a slight oversupply for teaching related occupations and paralegals/legal assistants. 


```{r, ft.align='left'}
gaps %>% flextable() %>% 
  width(j=1, width = 5) %>% 
  set_caption("Occupation Gaps over 10 Years in Greater Bay Area, Two-Year Degree or Higher Only", autonum = run_autonum(seq_id='tab', bkm='gaps')) %>% 
  footnote(j=1, value = as_paragraph("Source: JobsEQ, via Hanover Research"), ref_symbols=c(""), part = "header") %>% 
  footnote(j=1, value = as_paragraph("Note that this list only includes occupations that require at minimum a two-year (Associate's) degree. The Gap column illustrates the  number of persons with necessary credentials to work in these field."), ref_symbols=c(""), part = "header")

```

The occupations with the most job openings in the Greater Bay Area are Software Developers, Operations Managers, Project Management and Business Operations Specialists, and Accountants. 
```{r, ft.align="left"}
most_openings %>% select(-"Unemployment") %>% 
  flextable::flextable() %>% 
  set_caption("Occupations with the Most Job Openings", autonum = run_autonum(seq_id='tab', bkm='openings')) %>% 
  flextable::set_table_properties(width = .5, layout='autofit') %>% 
  footnote(j=1, value = as_paragraph("Source: JobsEQ, via Hanover Research"), ref_symbols=c(""), part = "header")

```

The fastest growing occupations are Information Security Analysts, Data Scientists and Medical and Health Services Managers.


```{r, ft.align="left"}
most_growth %>% select(-"Unemployment") %>% 
  flextable::flextable() %>% 
  flextable::set_formatter("% Change" = function(x) sprintf("%.001f%%", x*100)) %>%
  set_caption("Fastest Growing Occupations",autonum = run_autonum(seq_id='tab', bkm='topten')) %>% 
  width(j=1, width = 5) %>% 
  footnote(j=1, value = as_paragraph("Source: JobsEQ, via Hanover Research"), ref_symbols=c(""), part = "header")


```

Diversity varies across industries, with less representation for women and/or people of color in healthcare, technology, business services, public administration, and financial services. The Bureau of Labor Statistics' 2021 [population survey](https://www.bls.gov/cps/cpsaat18.htm) indicates that women make up less than half the workforce in many industries, with particularly low shares in manufacturing, architecture and engineering, and computer systems. Many women and underrepresented minorities report leaving tech jobs due to workplace unfairness. Although women make up a large share of the healthcare workforce, few have leadership roles. Further, racial and ethnic diversity in the healthcare industry is low.  

```{r, ft.align="left"}
#id_arch, id_comp, id_data, id_man, id_nav, id_semi
ind_div %>% arrange(Industry) %>% 
  flextable() %>%
  width(j = 1, width = 4.65) %>% 
  width(j = 2:3, width = .93) %>% 
  flextable::set_formatter("Percentage" = function(x) sprintf("%.001f%%", x*100)) %>% 
  set_caption("Diversity in Industries (Greater Bay Area, 2020 Q3)", autonum = run_autonum(seq_id='tab', bkm='divind')) %>% 
  footnote(j=1, value = as_paragraph("Source: JobsEQ, via Hanover Research"), ref_symbols=c(""), part = "header") %>% 
  surround(i = c(7, 13, 19, 25, 31), part = 'body', border.top = fp_border())

```



## Demographic Data 

Population projections indicate strong growth in Santa Clara County as well as the Greater Bay Area. Between 2020 and 2060 projections suggest the Greater Bay Area’s population will increase by 18.2 % Santa Clara County’s population growth is expected to be higher at 23.1%.

```{r, ft.align="left"}
projections %>% 
  pivot_wider(names_from = years, values_from = population) %>% 
  flextable::flextable() %>% 
  set_caption("Bay Area Population Projections", autonum = run_autonum(seq_id='tab', bkm='popproj')) %>% 
  width(width=1.05) %>% 
  footnote(j=1, value = as_paragraph("Source: State of California Department of Finance, via Hanover Research"), ref_symbols=c(""), part = "header")
```

Projections by age group suggest an aging population, though the traditional student age group is expected to remain stable. Projections through 2060 by age group indicate large increases in the share of residents ages 40-44 and 85+, with a small increase in the 35-39 age group. The share of residents below 20 is expected to decline. Ages 20-24, the prime college going population, is expected to remain between 7.6 and 7.7%.


```{r, ft.align="left"}
#population projection by age
ageproj %>% 
  flextable() %>% 
  set_caption("Bay Area Population Projections by Age",autonum = run_autonum(seq_id='tab', bkm='aproj')) %>% 
    footnote(j=1, value = as_paragraph("Source: State of California Department of Finance, via Hanover Research"), ref_symbols=c(""), part = "header")


```



Projections suggest an increasingly diverse community in the Greater Bay Area. A Metropolitan Transportation Commission (MTC) report on The Bay Area in 2040 suggests the population will become substantially more racially and ethnically diverse compared to the 2010 Census figures. Hispanic/Latino residents are projected to become the largest ethnic group and significant decline is projected in the White non Hispanic population. The share of Black or African American residents is also expected to decline slightly. Population projections in the Greater Bay Area suggest this trend will continue through 2060 with the share of non-Hispanic Whites dropping by 15.7% while the Asian population increases by 10.2%, and the Hispanic/Latino population grows by 4.8%. The Black non Hispanic population is expected to fall very slightly, by less than one percentage point.


```{r, ft.align="left"}
raceproj %>% 
  flextable::flextable() %>% 
  set_caption("Bay Area Population Projections by Race/Ethnicity",autonum = run_autonum(seq_id='tab', bkm='rproj')) %>% 
  flextable::set_formatter("2020" = function(x) sprintf("%.001f%%", x*100)) %>% 
  flextable::set_formatter("2060" = function(x) sprintf("%.001f%%", x*100)) %>% 
  flextable::set_formatter("Percent Change" = function(x) sprintf("%.001f%%", x*100)) %>% 
  width(j=1,width=3) %>% 
  footnote(j=1, value = as_paragraph("Source: State of California Department of Finance, via Hanover Research"), ref_symbols=c(""), part = "header")

```

The Greater Bay Area and the Santa Clara County are relatively diverse, but has a low share of Black or African American residents (5.5% and 2.3%, respectively). In the Greater Bay Area, the largest share of the population is White non Hispanic, while in the Santa Clara County, it is Asian. In both areas, approximately a quarter of residents are Hispanic or Latino (of any race). 
Latinx students comprise the largest percentage of the SJCC 2021 population, making up 40% of the student population compared to around 25% of both the Santa Clara County and greater Bay Area populations. Asian students are 30% of the SJCC population, which is higher than the greater Bay Area population (25%) but lower than the Santa Clara County population (35%). The percentage of Black SJCC students is comparable to the greater Bay Area's population percentage. 


```{r, ft.align="left"}
  ethnicity1 %>% flextable() %>% 
   set_caption("Service Area Ethnicity Breakdown, 2019",autonum = run_autonum(seq_id='tab', bkm='ethn')) %>% 
    flextable::set_formatter("Bay Area %" = function(x) sprintf("%.001f%%", x*100)) %>%
    flextable::set_formatter("Santa Clara County %" = function(x) sprintf("%.001f%%", x*100))%>%
    align(j=7, align = "right", part = "all") %>% 
    footnote(j=1, value = as_paragraph("Source: US Census Bureau, via Hanover Research"), ref_symbols=c(""), part = "header") %>% 
  footnote(j=1, value = as_paragraph("Note: SJCC Headcount data is the annual 2020-2021 overall headcount."), ref_symbols=c(""), part = "header")

#### please note the year of the data. -done
#### order based on the bay area percentage
### can you check that the white alone actually means white alone, not hispanic or Latino? - it does
#### let's add the 2020-2021 annual headcount (both credit and noncredit) by ethnicity as another column both n and %. Add a note below that says it is from 2020-2021 data. 


```




## Socio-economic Data 

On the whole, the Greater Bay Area and Santa Clara County is well-educated. More than a quarter of Greater Bay Area residents hold a bachelor’s degree, with nearly 20% holding a graduate or professional degree. A small share holds associate’s degrees, but it is unclear how many bachelor’s degree holders initially pursued an associate’s program before transfer. However, over 40% of Santa Clara County residents aged 25 or older hold less than associate degree.  

```{r, ft.align="left"}
educ_total %>% 
  flextable::flextable() %>% 
  set_caption("Educational Attainment for Population Age 25+, 2019",autonum = run_autonum(seq_id='tab', bkm='edatt')) %>% 
  flextable::set_formatter("Bay Area: Percent" = function(x) sprintf("%.001f%%", x*100)) %>% 
  flextable::set_formatter("Santa Clara County: Percent" = function(x) sprintf("%.001f%%", x*100)) %>% 
  flextable::set_table_properties(width = .5, layout='autofit') %>% 
  footnote(j=1, value = as_paragraph("Source: US Census Bureau, via Hanover Research"), ref_symbols=c(""), part = "header") %>% 
  surround(i = 9, part = 'body', border.top = fp_border(width = 1.2))

#### for total, use 100% instead of NA%. Also, add "Total" before the word population for the first row. -done

#### use a row separater to mark the last 2 rows in a way similar to Santa Barabara did it. As it is, it is a bit hard to understand what the last 2 rows are doing. I want to see a line or a row above high school separating the last 2 rows from the rest. - done

### is this data available by race if you go to census? If available, can you write a paragraph which population are experiencing lower educational attainment?

### add year information - done



```

The median and average household income in the Greater Bay Area is high and slightly higher in the Santa Clara County. Both are comparably much higher than the national median income. The median household income in Greater Bay Area counties for 2019 is \$97,986. Santa Clara County median household income is slightly higher at \$116,178.

```{r, ft.align="left"}
median1 %>% 
  flextable::flextable() %>% 
  set_caption("Household Income in the Service Area",autonum = run_autonum(seq_id='tab', bkm='income')) %>% 
  width(width=1.5) %>% 
    footnote(j=1, value = as_paragraph("Source: US Census Bureau (American Community Survey, 2014-2018), via Hanover Research"), ref_symbols=c(""), part = "header")

#### can  you make sure that the SC county data also goes down to the 2 decimal places. If unavailable, get rid of it for other columns too. - done


#### can you get this sort of income data by race to illustrate the income gap?
### also can you find out if by income we mean household income? - done


```

Poverty rates in the Santa Clara County and Greater Bay Area are lower than the state of California and the United States as a whole. Approximately 9.0% of Greater Bay Area residents between the ages of 18 and 64 are determined to be below the poverty level, lower than the share in California 12.3% and the United States 12.6%.

```{r, ft.align='left'}
poverty %>% flextable() %>%
    flextable::set_formatter("Greater Bay Area" = function(x) sprintf("%.001f%%", x*100)) %>% 
    flextable::set_formatter("Santa Clara County" = function(x) sprintf("%.001f%%", x*100)) %>% 
    set_caption("Poverty Level in the Service Area, 2019",autonum = run_autonum(seq_id='tab', bkm='poverty')) %>% 
  width(width=1.5) %>% 
  footnote(j=1, value = as_paragraph("Source: US Census Bureau, via Hanover Research"), ref_symbols=c(""), part = "header")


###also is this data available by race? - yes

```

However, the poverty level differs significantly by race. Approximately 18% of Black residents in the Greater Bay Area are determined to be below the poverty level, almost three times more compared to White residents. Similarly, American Indian and Alaska Native, Latinx and Pacific Islander residents also experienced higher rates of poverty compared to the Greater Bay Area average.

```{r, ft.align='left'}
#poverty by race
poverty_race1 %>% 
  flextable() %>% 
  set_caption("Poverty Level by Race in the Service Area, 2019",autonum = run_autonum(seq_id='tab', bkm='rpoverty')) %>% 
  width(j= 1, width=3.5) %>% 
  footnote(j=1, value = as_paragraph("Source: US Census Bureau, via Hanover Research"), ref_symbols=c(""), part = "header") %>% 
  align(j=c(2:3), align='right', part='all')
```


## Sites 

[List names and locations (including addresses) of sites where 50% or more of a program, certificate, or degree is available to students, and any other off-campus sites or centers.] 

## Specialized or Programmatic Accreditation 

[Provide a list of any specialized or programmatic accreditations held by the institution.] 