---
title: "ISER Data Section"
author: "Office of Reserach, Planning and Institutional Effectiveness"
date: "`r Sys.Date()`"
output: word_document
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(flextable)
library(officer)

load("../is_standards.RData")
load("../entable.RData")
load("../jobs.RData")
load("../demo.RData")
load("../labor_data.RData")
set_flextable_defaults(font.size = 9)

```


# Introduction

## College History

[Provide a brief history of the institution, including year of establishment. Highlight major events or developments that have occurred since the last comprehensive review.]

## Student Enrollment Data 

### Overall Enrollment Trend

The college's overall enrollment, using any enrollment metrics (headcount, seatcount or full-time equivalent students (FTES)), has declined in the last 5 years after a small increase in 2018-2019. Given the impact of COVID-19 pandemic and the statewide enrollment decline, this is not surprising.

Overall headcount has declined 16% from 2017-18 to 2021-22. This decline is reflected throughout the enrollment trend data.

>>>>> Calculate the percentage decline from 2017-18 for headcount and talk about that.

```{r, ft.align='left'}
annual %>% 
    filter(Metric == "Overall:" | Metric == "Credit Students:" | Metric == "Noncredit Students:" | Metric == "Headcount") %>% 
  flextable() %>% 
  set_caption("Annual Student Metrics", 
              autonum = run_autonum(seq_id='tab', bkm='hc')) %>% 
  footnote(j=1, value=as_paragraph("Source: SJCC Internal Data Warehouse"),
           ref_symbols=c(""), part = "header") %>% 
  width(j=1, width=2) %>% 
  #if including ftes and sc, these five lines need to be used so that they affect the subheadings
  # surround(i = 5, part = 'body', border.top = fp_border()) %>% 
  # surround(i = 9, part = 'body', border.top = fp_border()) %>% 
  # bold(i=1, part='body') %>% 
  # bold(i=5, part='body') %>%
  # bold(i=9, part='body') %>% 
  surround(i = 3, part = 'body', border.top = fp_border()) %>% 
  surround(i = 5, part = 'body', border.top = fp_border()) %>% 
  bold(i=1, part='body') %>% 
  bold(i=3, part='body') %>%
  bold(i=5, part='body') %>% 
  footnote(j=1, value=as_paragraph("A student is counted as credit/noncredit if they take at least one course in that type. Note that some students enroll in both credit and noncredit courses during the academic year, so they are included in both the credit and noncredit figures. Because of this, the sum of credit and noncredit headcounts does not equal the overall headcount."),
           ref_symbols=c(""), part = "header")
#### have the seatcount and FTES ready, but remove from the discussion here. We may put them back in later. Let me know if you have any questions on this.
```



### Credit Enrollment Trends and Student Composition

>>>>> let's separate out credit and noncredit. in this section only focus on credit students and their breakdown
>>>>> decribe the 5 year trend using 5yr %change, which sets the reference decline for examining all groups.
>>>>> add the average at the end here.

This section describes the credit enrollment trends by various student attributes. Data are from Fall terms between Fall 2017 and Fall 2021. It includes all students enrolled in at least one credit course. The data are extracted from the district's internal database by the Office of Research, Planning and Institutional Effectiveness. 

>>>> insert discussion of 5 year trend here.

```{r, ft.align='left'}
fall_hc %>% 
  pivot_wider(names_from="Fall Term", values_from = "Headcount") %>% 
  flextable() %>% 
  set_caption("Unduplicated Overall Headcount, Fall Terms", 
              autonum = run_autonum(seq_id='tab', bkm='fhc')) %>% 
  footnote(j=1, value=as_paragraph("Source: SJCC Internal Data Warehouse"),
           ref_symbols=c(""), part = "header") %>% 
  width(width=1)
```
>>>> Describe the trend you see here in a plain straightforward language. For example, "In Fall terms, xx percent of credit students are y type, xx percent are z type, etc. any other noteworthy obvious trends.



```{r, ft.align='left'}
fall_type %>% 
  flextable() %>% 
  set_caption("Unduplicated Headcount by Student Type, Fall Terms", 
              autonum = run_autonum(seq_id='tab', bkm='fthc')) %>% 
  footnote(j=1, value=as_paragraph("Source: SJCC Internal Data Warehouse"),
           ref_symbols=c(""), part = "header") %>%
  width(j=1, width=1.3) %>% 
  width(j=7, width=1) %>% 
  align(j=c(2:7), align = 'right', part = 'all')

```

>>> same thing here

```{r, ft.align='left'}
fall_goal %>% 
  #pivot_wider(names_from="Fall Term", values_from = "Headcount") %>% 
  flextable() %>% 
  set_caption("Unduplicated Credit Headcount by Student Goal, Fall Terms", 
              autonum = run_autonum(seq_id='tab', bkm='fghc')) %>% 
  footnote(j=1, value=as_paragraph("Source: SJCC Internal Data Warehouse"),
           ref_symbols=c(""), part = "header") %>% 
  width(j=1, width=2) %>% 
  align(j=c(2:7), align = 'right', part = 'all')
```

```{r, ft.align='left'}
fall_gender %>% 
  #pivot_wider(names_from="Fall Term", values_from = "Headcount") %>% 
  flextable() %>% 
  set_caption("Unduplicated Credit Headcount by Gender, Fall Terms", 
              autonum = run_autonum(seq_id='tab', bkm='fgehc')) %>% 
  footnote(j=1, value=as_paragraph("Source: SJCC Internal Data Warehouse"),
           ref_symbols=c(""), part = "header") %>% 
  width(j=7, width=1.1) %>% 
  align(j=c(2:7), align = 'right', part = 'all')
```


```{r, ft.align='left'}
fall_race %>% 
  #pivot_wider(names_from="Fall Term", values_from = "Headcount") %>% 
  flextable() %>% 
  set_caption("Unduplicated Credit Headcount by Race/Ethnicity, Fall Terms", 
              autonum = run_autonum(seq_id='tab', bkm='frhc')) %>% 
  footnote(j=1, value=as_paragraph("Source: SJCC Internal Data Warehouse"),
           ref_symbols=c(""), part = "header") %>% 
  width(j=1, width=1.6) %>% 
  align(j=c(2:7), align = 'right', part = 'all')
```

```{r, ft.align='left'}
fall_age %>% 
  #pivot_wider(names_from="Fall Term", values_from = "Headcount") %>% 
  flextable() %>% 
  set_caption("Unduplicated Credit Headcount by Age, Fall Terms", 
              autonum = run_autonum(seq_id='tab', bkm='fahc')) %>% 
  footnote(j=1, value=as_paragraph("Source: SJCC Internal Data Warehouse"),
           ref_symbols=c(""), part = "header") %>% 
  width(j=1, width=.8) %>% 
  width(j=7, width=1) %>% 
  align(j=c(2:7), align = 'right', part = 'all')
```



```{r, ft.align='left'}
sp_hc %>% flextable() %>% 
  set_caption("Unduplicated Headcount of Special Populations, Fall Terms", 
              autonum = run_autonum(seq_id='tab', bkm='special')) %>% 
  footnote(j=1, value=as_paragraph("Source: CCC Chancellor's Office Data Mart"),
           ref_symbols=c(""), part = "header") %>% 
  width(j=1, width=3)
```
### Noncredit Enrollment Trends and Student Composition

>>>>> for noncredit, only disaggregate by gender, race and age.
>>>> Also do this by subject area too where if they take one noncredit course in one subject area, then count that as enrollment in that subject area. The point I want to make is that the biggest program is our noncredit esl.

```{r, ft.align='left'}
#gender
fall_ncgender %>% 
  flextable() %>% 
  set_caption("Noncredit Headcount by Gender, Fall Terms", 
              autonum = run_autonum(seq_id='tab', bkm='fgehcnc')) %>% 
  footnote(j=1, value=as_paragraph("Source: SJCC Internal Data Warehouse"),
           ref_symbols=c(""), part = "header") %>% 
  width(j=7,width=1.1) %>% 
  align(j=c(2:7), align = 'right', part = 'all')



```


```{r, ft.align='left'}
#race
fall_ncrace %>% 
  flextable() %>% 
  set_caption("Noncredit Headcount by Race/Ethnicity, Fall Terms", 
              autonum = run_autonum(seq_id='tab', bkm='frhcnc')) %>% 
  footnote(j=1, value=as_paragraph("Source: SJCC Internal Data Warehouse"),
           ref_symbols=c(""), part = "header") %>% 
  width(j=7,width=1.1) %>% 
  width(j=1,width=1.6) %>% 
  align(j=c(2:7), align = 'right', part = 'all')

```


```{r, ft.align='left'}
#age
fall_ncage %>% 
  flextable() %>% 
  set_caption("Noncredit Headcount by Age, Fall Terms", 
              autonum = run_autonum(seq_id='tab', bkm='fahcnc')) %>% 
  footnote(j=1, value=as_paragraph("Source: SJCC Internal Data Warehouse"),
           ref_symbols=c(""), part = "header") %>% 
  width(j=7,width=1.1) %>% 
  width(j=1,width=.9) %>% 
  align(j=c(2:7), align = 'right', part = 'all')

```


```{r, ft.align='left'}
#subject area (split crs_name into dept, #)
fall_ncsubject %>% 
  flextable() %>% 
  set_caption("Noncredit Headcount by Subject, Fall Terms", 
              autonum = run_autonum(seq_id='tab', bkm='fahc')) %>% 
  footnote(j=1, value=as_paragraph("Source: SJCC Internal Data Warehouse"),
           ref_symbols=c(""), part = "header") %>% 
  width(j=7,width=1.1) %>% 
  align(j=c(2:7), align = 'right', part = 'all')

```


## Labor Market Data 

At a broad level, the top industries in the Greater Bay Area are Health Care and Social Assistance and Professional, Scientific, and Technical Services.

```{r, ft.align='left'}
broad_ten %>% flextable() %>% 
  flextable::set_formatter("Share of Total Employment" = function(x) sprintf("%.001f%%", x*100)) %>% 
  set_caption("Top Industries by Employment (Greater Bay Area, 2020 Q3)", autonum = run_autonum(seq_id='tab', bkm='broadten')) %>% 
  footnote(j=1, value = as_paragraph("Source: JobsEQ, via Hanover Research"), ref_symbols=c(""), part = "header") %>% 
  width(j=1, width = 4.5) %>% 
  width(j=2, width=2)
```

More than 10 percent of workers are employed in each of these two broad industries. At a more detailed level, employment after restaurants is concentrated in several high tech industries, schools, and hospitals (reference the top industries by employment table). 

```{r, ft.align="left"}
topten %>% flextable::flextable() %>% 
  flextable::set_formatter("Share of Total Employment" = function(x) sprintf("%.001f%%", x*100)) %>% 
  width(j=1, width = 4.5) %>% 
  width(j=2, width=2) %>% 
  set_caption("Top Industries by Employment  (Greater Bay Area, 2020 Q3)", autonum = run_autonum(seq_id='tab', bkm='topten')) %>% 
  footnote(j=1, value = as_paragraph("Source: JobsEQ, via Hanover Research"), ref_symbols=c(""), part = "header")
```

All top 10 Bay Area tech industries by share of employment have positive 10-year projected growth (reference table). Also, the Greater Bay Area is projected to have an employment undersupply for occupations in business, technology, and healthcare including software developers, nurses, and managers while it is also projected to have a slight oversupply for teaching related occupations and paralegals/legal assistants. 


```{r, ft.align='left'}
gaps %>% flextable() %>% 
  width(j=1, width = 5) %>% 
  set_caption("Occupation Gaps over 10 Years in Greater Bay Area, Two-Year Degree or Higher Only", autonum = run_autonum(seq_id='tab', bkm='gaps')) %>% 
  footnote(j=1, value = as_paragraph("Source: JobsEQ, via Hanover Research"), ref_symbols=c(""), part = "header") %>% 
  footnote(j=1, value = as_paragraph("Note that this list only includes occupations that require at minimum a two-year (Associate's) degree."), ref_symbols=c(""), part = "header")

```



```{r, ft.align="left"}
toptech %>% flextable::flextable() %>% 
  set_caption("Top Bay Area Tech Industries  (Greater Bay Area, 2020 Q3)", autonum = run_autonum(seq_id='tab', bkm='toptech')) %>% 
  flextable::set_formatter("Projected Growth, 2020-2030" = function(x) sprintf("%.001f%%", x*100)) %>% 
  flextable::set_formatter("Share of Total Employment" = function(x) sprintf("%.001f%%", x*100)) %>% 
  flextable::set_table_properties(width = .5, layout='autofit') %>% 
  footnote(j=1, value = as_paragraph("Source: JobsEQ, via Hanover Research"), ref_symbols=c(""), part = "header")

```
```{r, ft.align="left"}
most_openings %>% select(-"Unemployment") %>% 
  flextable::flextable() %>% 
  set_caption("Occupations with the Most Job Openings", autonum = run_autonum(seq_id='tab', bkm='openings')) %>% 
  flextable::set_table_properties(width = .5, layout='autofit') %>% 
  footnote(j=1, value = as_paragraph("Source: JobsEQ, via Hanover Research"), ref_symbols=c(""), part = "header")

```

```{r, ft.align="left"}
most_growth %>% select(-"Unemployment") %>% 
  flextable::flextable() %>% 
  flextable::set_formatter("% Change" = function(x) sprintf("%.001f%%", x*100)) %>%
  set_caption("Fastest Growing Occupations",autonum = run_autonum(seq_id='tab', bkm='topten')) %>% 
  width(j=1, width = 5) %>% 
  footnote(j=1, value = as_paragraph("Source: JobsEQ, via Hanover Research"), ref_symbols=c(""), part = "header")


```


## Demographic Data 

[Provide summary-level demographic data for the service area. Disaggregate the data as appropriate for the institution’s mission and service area. Provide brief context if needed.] 


```{r, ft.align="left"}
projections %>% 
  pivot_wider(names_from = years, values_from = population) %>% 
  flextable::flextable() %>% 
  set_caption("Bay Area Population Projections", autonum = run_autonum(seq_id='tab', bkm='popproj')) %>% 
  width(width=1.05) %>% 
  footnote(j=1, value = as_paragraph("Source: State of California Department of Finance, via Hanover Research"), ref_symbols=c(""), part = "header")
```


```{r, ft.align="left"}
raceproj %>% 
  flextable::flextable() %>% 
  set_caption("Bay Area Population Projections by Race/Ethnicity",autonum = run_autonum(seq_id='tab', bkm='rproj')) %>% 
  flextable::set_formatter("2020" = function(x) sprintf("%.001f%%", x*100)) %>% 
  flextable::set_formatter("2060" = function(x) sprintf("%.001f%%", x*100)) %>% 
  flextable::set_formatter("Percent Change" = function(x) sprintf("%.001f%%", x*100)) %>% 
  width(j=1,width=3) %>% 
  footnote(j=1, value = as_paragraph("Source: State of California Department of Finance, via Hanover Research"), ref_symbols=c(""), part = "header")

```

```{r, ft.align="left"}
race %>% flextable::flextable() %>% 
    flextable::set_caption("Service Area Racial Breakdown",autonum = run_autonum(seq_id='tab', bkm='race')) %>%     flextable::set_formatter("Bay Area: Percent" = function(x) sprintf("%.001f%%", x*100)) %>% 
    flextable::set_formatter("SC County: Percent" = function(x) sprintf("%.001f%%", x*100))%>% 
  flextable::set_table_properties(width = .5, layout='autofit') %>% 
  footnote(j=1, value = as_paragraph("Source: US Census Bureau, via Hanover Research"), ref_symbols=c(""), part = "header")


#### for SC County, either spell it out Santa Clara or put it in notes. Acronyms are to be avoided in ISER.



```

```{r, ft.align="left"}
  ethnicity %>% flextable::flextable() %>% 
    set_caption("Service Area Ethnicity Breakdown",autonum = run_autonum(seq_id='tab', bkm='ethn')) %>% 
    flextable::set_formatter("Bay Area: Percent" = function(x) sprintf("%.001f%%", x*100)) %>% 
    flextable::set_formatter("SC County: Percent" = function(x) sprintf("%.001f%%", x*100))%>% 
    flextable::set_table_properties(width = .5, layout='autofit') %>% 
    footnote(j=1, value = as_paragraph("Source: US Census Bureau, via Hanover Research"), ref_symbols=c(""), part = "header")

```




## Socio-economic Data 

[Provide summary-level socio-economic data for the service area. Disaggregate the data as appropriate for the institution’s mission and service area. Provide brief context if needed.] 

```{r, ft.align="left"}
education %>% 
  flextable::flextable() %>% 
  set_caption("Educational Attainment for Population Age 25+",autonum = run_autonum(seq_id='tab', bkm='edatt')) %>% 
  flextable::set_formatter("Bay Area: Percent" = function(x) sprintf("%.001f%%", x*100)) %>% 
  flextable::set_formatter("SC County: Percent" = function(x) sprintf("%.001f%%", x*100)) %>% 
  flextable::set_table_properties(width = .5, layout='autofit') %>% 
  footnote(j=1, value = as_paragraph("Source: US Census Bureau, via Hanover Research"), ref_symbols=c(""), part = "header") %>% 
  surround(i = 9, part = 'body', border.top = fp_border(width = 1.2))

#### for total, use 100% instead of NA%. Also, add "Total" before population for the first row.

#### use a row separater to mark the last 2 rows in a way similar to Santa Barabara did it. As it is, it is a bit hard to understand what the last 2 rows are doing. I want to see a line or a row above high school separating the last 2 rows from the rest. 



```


```{r, ft.align="left"}
median[1,1] <- "Median Income (dollars)"
median %>% 
  flextable::flextable() %>% 
  set_caption("Income in the Service Area",autonum = run_autonum(seq_id='tab', bkm='income')) %>% 
  width(width=1.5) %>% 
    footnote(j=1, value = as_paragraph("Source: US Census Bureau, via Hanover Research"), ref_symbols=c(""), part = "header")

#### can  you make sure that the SC county data also goes down to the 2 decimal places. If unavailable, get rid of it for other columns too.


#### can you get this sort of income data by race to illustrate the income gap?
### also can you find out if by income we mean household income? 


```


```{r, ft.align='left'}
poverty %>% flextable() %>%
    flextable::set_formatter("Greater Bay Area" = function(x) sprintf("%.001f%%", x*100)) %>% 
    flextable::set_formatter("Santa Clara County" = function(x) sprintf("%.001f%%", x*100)) %>% 
    set_caption("Poverty Level in the Service Area",autonum = run_autonum(seq_id='tab', bkm='poverty')) %>% 
  width(width=1.5) %>% 
  footnote(j=1, value = as_paragraph("Source: US Census Bureau, via Hanover Research"), ref_symbols=c(""), part = "header")


###also is this data available by race?

```


## Sites 

[List names and locations (including addresses) of sites where 50% or more of a program, certificate, or degree is available to students, and any other off-campus sites or centers.] 

## Specialized or Programmatic Accreditation 

[Provide a list of any specialized or programmatic accreditations held by the institution.] 

# Presentation of Student Achievement Data and Institution-Set Standards 


```{r, ft.align='left'}
desc <- overallcs$description[1]
overallcs %>% 
  select(years, Type, percentage) %>% 
  pivot_wider(names_from = years, values_from = percentage) %>% 
  flextable::flextable() %>% 
  flextable::align(i=1, align="center", part="header") %>% 
  flextable::set_formatter("2016-2017" = function(x) sprintf("%.001f%%", x*100)) %>% 
  flextable::set_formatter("2017-2018" = function(x) sprintf("%.001f%%", x*100)) %>% 
  flextable::set_formatter("2018-2019" = function(x) sprintf("%.001f%%", x*100)) %>% 
  flextable::set_formatter("2019-2020" = function(x) sprintf("%.001f%%", x*100)) %>% 
  width(width = 1.3) %>% 
  align(j=1, align= "left", part = "all") %>% 
  align(j=2:5, align = "right", part = "all") %>% 
  set_caption("Overall Course Success Rate",autonum = run_autonum(seq_id='tab', bkm='cso')) %>%
  footnote(j=1, value = as_paragraph("Source: Student Success Metrics"), ref_symbols=c(""), part = "header")

```

```{r, ft.align='left'}
title <- "Distinct number of CO-approved certificate earners (12+ units)"
overall603 %>% 
  select(years, Type, value) %>% 
  pivot_wider(names_from = years, values_from = value) %>% 
  flextable::flextable() %>% 
  flextable::align(i=1, align="center", part="header") %>% 
  flextable::width(width=1.3) %>% 
  align(j=1, align= "left", part = "all") %>% 
  align(j=2:5, align = "right", part = "all") %>% 
  set_caption(title, autonum = run_autonum(seq_id='tab', bkm='cert')) %>%
  footnote(j=1, value = as_paragraph("Source: Student Success Metrics"), ref_symbols=c(""), part = "header")

```


```{r, ft.align='left'}
title <- "Distinct number of degree earners (AA, AS, or ADT) "
overall631 %>% 
  select(years, Type, value) %>% 
  pivot_wider(names_from = years, values_from = value) %>% 
  flextable::flextable() %>% 
  flextable::align(i=1, align="center", part="header") %>%
  align(j=1, align= "left", part = "all") %>% 
  align(j=2:5, align = "right", part = "all") %>% 
  flextable::width(width=1.3) %>% 
  set_caption(title, autonum = run_autonum(seq_id='tab', bkm='deg')) %>%
  footnote(j=1, value = as_paragraph("Source: Student Success Metrics"), ref_symbols=c(""), part = "header")
```

```{r, ft.align='left'}
title <- "Distinct number of ADT earners"
overall608 %>% 
  select(years, Type, value) %>% 
  pivot_wider(names_from = years, values_from = value) %>% 
  flextable::flextable() %>% 
  flextable::align(i=1, align="center", part="header") %>% 
  flextable::width(width=1.3) %>%
  align(j=1, align= "left", part = "all") %>% 
  align(j=2:5, align = "right", part = "all") %>% 
  set_caption(title, autonum = run_autonum(seq_id='tab', bkm='adt')) %>%
  footnote(j=1, value = as_paragraph("Source: Student Success Metrics"), ref_symbols=c(""), part = "header")

```


```{r, ft.align='left'}
title <- "Distinct number of transfers to CSU or UC"
overall614 %>% 
  select(years, Type, value) %>% 
  pivot_wider(names_from = years, values_from = value) %>% 
  flextable::flextable() %>% 
  flextable::align(i=1, align="center", part="header") %>% 
  flextable::width(width=1.1) %>% 
  align(j=1, align= "left", part = "all") %>% 
  align(j=2:6, align = "right", part = "all") %>% 
  set_caption(title, autonum = run_autonum(seq_id='tab', bkm='csuuc')) %>%
  footnote(j=1, value = as_paragraph("Source: Student Success Metrics"), ref_symbols=c(""), part = "header")
```
## Disaggregation by Gender


```{r, ft.align='left'}
title <- "Course Success Rates by Gender"
desc <- "Note: \"All Masked Values\" contains Non-Binary and Unknown/Non-Respondent students."
csgender %>% 
  select(years, Gender, value) %>% 
  drop_na() %>% 
  pivot_wider(names_from = years, values_from = value) %>% 
  flextable::flextable() %>% 
  flextable::align(i=1, align="center", part="header") %>% 
  flextable::set_formatter("2016-2017" = function(x) sprintf("%.001f%%", x*100)) %>% 
  flextable::set_formatter("2017-2018" = function(x) sprintf("%.001f%%", x*100)) %>% 
  flextable::set_formatter("2018-2019" = function(x) sprintf("%.001f%%", x*100)) %>% 
  flextable::set_formatter("2019-2020" = function(x) sprintf("%.001f%%", x*100)) %>% 
  flextable::add_footer_lines(values = desc) %>% 
  align(j=1, align= "left", part = "all") %>% 
  align(j=2:5, align = "right", part = "all") %>% 
  flextable::width(width=1.3) %>% 
  set_caption(title, autonum = run_autonum(seq_id='tab', bkm='csg')) %>%
  footnote(j=1, value = as_paragraph("Source: Student Success Metrics"), ref_symbols=c(""), part = "header")
```

```{r, ft.align='left'}
title <- "Certificate Earners by Gender"
desc <- "Note: \"All Masked Values\" contains Non-Binary and Unknown/Non-Respondent students."
ggrads603 %>% 
  select(years, Gender, value) %>% 
  drop_na() %>% 
  pivot_wider(names_from = years, values_from = value) %>% 
  flextable::flextable() %>% 
  flextable::align(i=1, align="center", part="header") %>% 
  flextable::width(width=1.3) %>% 
  align(j=1, align= "left", part = "all") %>% 
  align(j=2:5, align = "right", part = "all") %>% 
  flextable::add_footer_lines(values = desc) %>% 
  set_caption(title, autonum = run_autonum(seq_id='tab', bkm='certg')) %>%
  footnote(j=1, value = as_paragraph("Source: Student Success Metrics"), ref_symbols=c(""), part = "header")

```


```{r, ft.align='left'}
title <- "Degree Earners by Gender"
desc <- "Note: \"All Masked Values\" contains Non-Binary and Unknown/Non-Respondent students."
ggrads631%>% 
  select(years, Gender, value) %>% 
  drop_na() %>% 
  pivot_wider(names_from = years, values_from = value) %>% 
  flextable::flextable() %>% 
  flextable::align(i=1, align="center", part="header") %>% 
  flextable::add_footer_lines(values = desc) %>% 
  flextable::width(width=1.3) %>% 
  align(j=1, align= "left", part = "all") %>% 
  align(j=2:5, align = "right", part = "all") %>% 
  set_caption(title, autonum = run_autonum(seq_id='tab', bkm='degg')) %>%
  footnote(j=1, value = as_paragraph("Source: Student Success Metrics"), ref_symbols=c(""), part = "header")

```

```{r, ft.align='left'}
title <- "ADT Earners by Gender"
desc <- "Note: \"All Masked Values\" contains Non-Binary and Unknown/Non-Respondent students."
ggrads608%>% 
  select(years, Gender, value) %>% 
  drop_na() %>% 
  pivot_wider(names_from = years, values_from = value) %>% 
  flextable::flextable() %>% 
  flextable::align(i=1, align="center", part="header") %>% 
  flextable::add_footer_lines(values = desc) %>% 
  flextable::width(width=1.3) %>% 
  align(j=1, align= "left", part = "all") %>% 
  align(j=2:5, align = "right", part = "all") %>% 
  set_caption(title, autonum = run_autonum(seq_id='tab', bkm='adtg')) %>%
  footnote(j=1, value = as_paragraph("Source: Student Success Metrics"), ref_symbols=c(""), part = "header")

```


```{r, ft.align='left'}
title <- "Distinct Number of Transfers to CSU or UC by Gender"
desc <- "Note: \"All Masked Values\" contains Non-Binary and Unknown/Non-Respondent students."
ggrads614 %>% 
  select(years, Gender, value) %>% 
  filter(Gender=="Female" | Gender=="Male" | Gender=="All Masked Values") %>% 
  pivot_wider(names_from = years, values_from = value) %>% 
  flextable::flextable() %>% 
  flextable::align(i=1, align="center", part="header") %>% 
  flextable::add_footer_lines(values = desc) %>% 
  flextable::width(width=1.075) %>% 
  align(j=1, align= "left", part = "all") %>% 
  align(j=2:6, align = "right", part = "all") %>% 
  set_caption(title, autonum = run_autonum(seq_id='tab', bkm='csuucg')) %>%
  footnote(j=1, value = as_paragraph("Source: Student Success Metrics"), ref_symbols=c(""), part = "header")

```
## Disaggregation by Ethnicity

```{r, ft.align='left'}
title <- "Course Success Rates by Ethnicity"
desc <- "Note: \"All Masked Values\" contains students who listed another ethnicity or did not respond."
csrace %>% 
  select(years, Ethnicity, value) %>% 
  pivot_wider(names_from = years, values_from = value) %>% 
  drop_na() %>% 
  flextable::flextable() %>% 
  flextable::align(i=1, align="center", part="header") %>% 
  flextable::set_formatter("2016-2017" = function(x) sprintf("%.001f%%", x*100)) %>% 
  flextable::set_formatter("2017-2018" = function(x) sprintf("%.001f%%", x*100)) %>% 
  flextable::set_formatter("2018-2019" = function(x) sprintf("%.001f%%", x*100)) %>% 
  flextable::set_formatter("2019-2020" = function(x) sprintf("%.001f%%", x*100)) %>% 
  flextable::add_footer_lines(values = desc) %>% 
  flextable::width(j=1, width=2.1) %>% 
  align(j=1, align= "left", part = "all") %>% 
  align(j=2:5, align = "right", part = "all") %>% 
  set_caption(title, autonum = run_autonum(seq_id='tab', bkm='cse')) %>%
  footnote(j=1, value = as_paragraph("Source: Student Success Metrics"), ref_symbols=c(""), part = "header")

```


```{r, ft.align='left'}
title <- "Certificate Earners by Ethnicity"
desc <- "Note: \"All Masked Values\" contains students who listed another ethnicity or did not respond."
rgrads603 %>% 
  select(years, Ethnicity, value) %>% 
  #drop_na() %>% 
  pivot_wider(names_from = years, values_from = value) %>% 
  flextable::flextable() %>% 
  flextable::align(i=1, align="center", part="header") %>% 
  flextable::width(j=1, width=2.1) %>% 
  width(j=2:5, width = 1) %>% 
  flextable::add_footer_lines(values = desc) %>% 
  align(j=1, align= "left", part = "all") %>% 
  align(j=2:5, align = "right", part = "all") %>% 
  set_caption(title, autonum = run_autonum(seq_id='tab', bkm='certe')) %>%
  footnote(j=1, value = as_paragraph("Source: Student Success Metrics"), ref_symbols=c(""), part = "header")
```


```{r, ft.align='left'}
title <- "Degree Earners by Ethnicity"
desc <- "Note: \"All Masked Values\" contains students who listed another ethnicity or did not respond."
rgrads631%>% 
  select(years, Ethnicity, value) %>% 
  #drop_na() %>% 
  pivot_wider(names_from = years, values_from = value) %>% 
  flextable::flextable() %>% 
  flextable::align(i=1, align="center", part="header") %>% 
  flextable::width(j=1, width=2.2) %>% 
  width(j=2:5, width = 1) %>% 
  flextable::add_footer_lines(values = desc) %>% 
  align(j=1, align= "left", part = "all") %>% 
  align(j=2:5, align = "right", part = "all") %>% 
  set_caption(title, autonum = run_autonum(seq_id='tab', bkm='dege')) %>%
  footnote(j=1, value = as_paragraph("Source: Student Success Metrics"), ref_symbols=c(""), part = "header")
```


```{r, ft.align='left'}
title <- "ADT Earners by Ethnicity"
desc <- "Note: \"All Masked Values\" contains students who listed another ethnicity or did not respond."
rgrads608%>% 
  select(years, Ethnicity, value) %>% 
  #drop_na() %>% 
  pivot_wider(names_from = years, values_from = value) %>% 
  flextable::flextable() %>% 
  flextable::align(i=1, align="center", part="header") %>% 
  flextable::width(j=1, width=2.3) %>% 
  width(j=2:5, width = 1) %>% 
  flextable::add_footer_lines(values = desc) %>% 
  align(j=1, align= "left", part = "all") %>% 
  align(j=2:5, align = "right", part = "all") %>% 
  set_caption(title, autonum = run_autonum(seq_id='tab', bkm='adte')) %>%
  footnote(j=1, value = as_paragraph("Source: Student Success Metrics"), ref_symbols=c(""), part = "header")

```


```{r, ft.align='left'}
title <- "Distinct Number of Transfers to CSU or UC by Ethnicity"
desc <- "Note: \"All Masked Values\" contains students who listed another ethnicity or not respond."
rgrads614 %>% 
  select(years, Ethnicity, value) %>% 
  pivot_wider(names_from = years, values_from = value) %>% 
  flextable::flextable() %>% 
  flextable::align(i=1, align="center", part="header") %>% 
  flextable::width(j=1, width=2.2) %>% 
  flextable::add_footer_lines(values = desc) %>% 
  align(j=1, align= "left", part = "all") %>% 
  align(j=2:6, align = "right", part = "all") %>% 
  set_caption(title, autonum = run_autonum(seq_id='tab', bkm='csuuce')) %>%
  footnote(j=1, value = as_paragraph("Source: Student Success Metrics"), ref_symbols=c(""), part = "header")

```

## Licensure Pass and Job Placement Rates

```{r licensure, ft.align='left'}
licensure %>% 
  select("Program", "Exam Type", "Institution Set Standard", "Stretch Goal", 
         "2016-2017", "2017-2018", "2018-2019", "2019-2020", "2020-2021") %>% 
  flextable::flextable() %>% 
  flextable::set_table_properties(width = .5, layout='autofit') %>% 
  flextable::align(i=1, align="center", part="header") %>% 
  flextable::set_formatter("Institution Set Standard" = function(x) sprintf("%.001f%%", x*100)) %>%
  flextable::set_formatter("Stretch Goal" = function(x) sprintf("%.000f%%", x*100)) %>%
  flextable::set_formatter("2016-2017" = function(x) sprintf("%.000f%%", x*100)) %>% 
  flextable::set_formatter("2017-2018" = function(x) sprintf("%.000f%%", x*100)) %>% 
  flextable::set_formatter("2018-2019" = function(x) sprintf("%.000f%%", x*100)) %>% 
  flextable::set_formatter("2019-2020" = function(x) sprintf("%.000f%%", x*100)) %>% 
  flextable::set_formatter("2020-2021" = function(x) sprintf("%.000f%%", x*100)) %>% 
  footnote(i=4, j=8, value = as_paragraph("No campus specific data on this item."), ref_symbols = c("A"), part = "body") %>%  
  footnote(i=5, j=8, value = as_paragraph("No one took the exam this year due to Covid"), ref_symbols = c("B"), part = "body") %>% 
  set_caption("Licensure Pass Rates", autonum = run_autonum(seq_id='tab', bkm='cert')) %>%
  footnote(j=1, value = as_paragraph("Source: ACCJC Annual Reports"), ref_symbols=c(""), part = "header")


```


```{r job placement, ft.align='left'}
jobplace %>% 
  select("Program", "Institution Set Standard", "Stretch Goal", 
         "2018-2019", "2019-2020", "2020-2021") %>% 
  flextable() %>%
  flextable::set_formatter("Institution Set Standard" = function(x) sprintf("%.001f%%", x*100)) %>%
  flextable::set_formatter("Stretch Goal" = function(x) sprintf("%.000f%%", x*100)) %>%
  flextable::set_formatter("2018-2019" = function(x) sprintf("%.000f%%", x*100)) %>% 
  flextable::set_formatter("2019-2020" = function(x) sprintf("%.000f%%", x*100)) %>% 
  flextable::set_formatter("2020-2021" = function(x) sprintf("%.000f%%", x*100)) %>% 
  flextable::align(i=1, align="center", part="header") %>% 
  flextable::width(width=1.1) %>% 
  set_caption("Job Placement Rates", autonum = run_autonum(seq_id='tab', bkm='cert')) %>%
  footnote(j=1, value = as_paragraph("Source: ACCJC Annual Reports"), ref_symbols=c(""), part = "header") %>% 
  footnote(j=1, value = as_paragraph("Note that data is only available for 2018-2019 and years after."), ref_symbols=c(""), part = "header")


```
